---
title: "Deployment to Shiny Server and shinyapps.io"
output: 
  github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

To deploy a **corporaexplorer** app with your own data (corporaexplorerobject) to a
*[Shiny Server](https://rstudio.com/products/shiny/shiny-server/)* or 
*[shinyapps.io](https://www.shinyapps.io/)*
is incredibly simple -- all it takes is a folder with two files and three lines of code.

Example folder structure of the folder "my_app":

```
my_app  
  |  
  |-- app.R  
  |-- saved_corporaexplorerobject.rds  
```

Where "app.R" contains this code:

```{r eval=FALSE, include=TRUE}
library(corporaexplorer)
corpus <- readRDS("saved_corporaexplorerobject.rds")
explore(corpus)
```

The folder "my_app" is now ready to be hosted on a *Shiny Server* or be uploaded to *shinyapps.io*.

<hr>

*Tip 1: use the settings in the* `plot_options` *argument in* `explore()` *to fine-tune the appearance of the plots in the app.*  
*Tip 2: to make the data load faster (at the cost of occupying more disk space), save the corporaexplorerobject created by* `prepare_data()` *uncompressed by setting* `compress = FALSE` *in* `saveRDS()`.

*Example (assuming you start with a data frame called df):*

```{r eval=FALSE, include=TRUE}
library(corporaexplorer)
corpus <- prepare_data(df)
saveRDS(corpus, "saved_corporaexplorerobject.rds", compress = FALSE)
```
