---
title: "Demo app: State of the Union addresses"
output: 
  github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

To run the State of the Union demo app,
run the following in the R console:

```{r eval=FALSE, include=TRUE}
library(corporaexplorer)
run_sotu_app()
```

To run an alternative State of the Union app,
organised by decade rather than by president,
run the following in the R console:

```{r eval=FALSE, include=TRUE}
library(corporaexplorer)
run_sotu_decade_app()
```

These two apps are created with the code below.
The State of the Union texts and metadata are accessed through the
[**sotu**](https://cran.r-project.org/web/packages/sotu/index.html) package.

## Step 1: Preprocessing before "corporaexplorer"

**Loading packages**

```{r message=FALSE}
library(sotu)
library(stringr)
library(corporaexplorer)
```

**Creating data frame**

```{r}
## Merge data from 'sotu' package into one df
df <- sotu::sotu_meta
df$Text <- sotu::sotu_text %>%
    stringr::str_trim()

## Avoid clutter in corpus plot
# A. Distinguish between non-consecutive terms
df$president[97:100] <- "Grover Cleveland 1"
df$president[105:108] <- "Grover Cleveland 2"

# B. Get correct order of rows in data frame
    # in the cases where incumbent holds a final sotu before leaving office,
    # resulting in two sotus in one year
presidents <- unique(df$president)
df$president <- factor(df$president, levels = presidents)
df <- df[order(df$president),]
df$president <- as.character(df$president)

## Add decade variable for variation of app
df$decade <- stringr::str_sub(df$year, 1, 3) %>%
    paste0("0s")

# And add variable for informative document tab title in that app variation
df$for_tab_title <- paste(df$president, df$year)
```

## Step 2: Creating app with "corporaexplorer"

### App 1: State of the Union addresses grouped by president

**Create 'corporaexplorerobject'**

```{r message=FALSE}
corpus <- prepare_data(
    df,                                # the data frame created above
    date_based_corpus = FALSE,         # dates are not the organising principle in the corpus
    grouping_variable = "president",   # group the sotu addresses by president

# The remaining arguments are not strictly necessary, but we use them to fine-tune
      # how the corpus will be presented in the app

    within_group_identifier = "year",  # The tab header in document view will then be e.g. 
                                         # "Theodore Roosevelt – 1901"
    columns_doc_info =                 # metadata to be included in a "Document info" tab,
        colnames(df)[1:5],               # in this case the first five columns in the data frame
    tile_length_range = c(2, 10),      # fine-tuning the length of the tiles representing
                                         # the length of the addrsses
    use_matrix = FALSE                 # we don't create a document term matrix, as the corpus
                                         # is very small and searches will be fast anyway
)
```

**Run app**

```{r eval=FALSE, include=TRUE}
run_corpus_explorer(corpus)
```

<hr>

### App 2: State of the Union addresses grouped by decade

By just changing two arguments (or even one), we create an app with a quite different
organisation of the texts.

```{r message=FALSE}
corpus <- prepare_data(
    df,
    date_based_corpus = FALSE,
    grouping_variable = "decade",                # change grouping variable
    within_group_identifier = "for_tab_title",   # adjust tab header in document view
    columns_doc_info =
        colnames(df)[1:5],
    tile_length_range = c(2, 10),
    use_matrix = FALSE
)
```

```{r eval=FALSE, include=TRUE}
run_corpus_explorer(corpus)
```


## Examples of app adjustments

See the documentation for `run_corpus_explorer()` for all runtime options.

**Example 1: Tile length**
By default, the length of the tiles representing documents in the app
have varying lengths, depending on document length.
For all tiles to of the same length:

```{r eval=FALSE, include=TRUE}
run_corpus_explorer(corpus,
                    plot_options = list(
                        tile_length = "uniform"
                    ))
```

**Example 2: Plot colours**
To change the use of colours in the corpus map,
use e.g.:

```{r eval=FALSE, include=TRUE}
run_corpus_explorer(corpus,
                    plot_options = list(
                        colours = "green"
                    ))
```


## Examples of app usage

Some `run_corpus_explorer()` calls with
pre-filled sidebar input:

```{r eval=FALSE, include=TRUE}
run_corpus_explorer(corpus,
                    search_input = list(
                        search_terms = c("socialis",
                                         "communis",
                                         "soviet")
                    ))
```

```{r eval=FALSE, include=TRUE}
run_corpus_explorer(corpus,
                    search_input = list(
                        filter_terms = "speech--sotu_type"
                    ))
```

```{r eval=FALSE, include=TRUE}
run_corpus_explorer(corpus,
                    search_input = list(
                        search_terms = c("democracy",
                                         "freedom",
                                         "democratic--party"),
                        filter_terms = "speech--sotu_type"
                    ))
```
